% E. Dunham -- Resume
% Contents Copyright (C) 2014 - 2016, E. Dunham

% LaTeX code for rendering the resume is distributed under the MIT license.
% See LICENSE.txt. It means you can use the code for whatever you want,
% including your own resume, but I'm not liable if it catches your computer on
% fire.

% Template originally developed by E. Dunham
% https://github.com/edunham/resume/blob/master/resume.tex

\documentclass[11pt]{article} % Set default font size to 11pt


% Some settings that the stuff hidden in the preamble will reference
\def \whitespaciness { 0 } % pt. bigger numbers = emptier page. 0 is ok.
\def \typeoffill {\dotfill} % hfill makes blank, dotfill makes dotted lines.


\input{preamble}
\begin{document}

\centerline{{\Huge \bf Ahmed Jama}}

\bigskip

\contact{resume@ahmedjama.com}
        {ahmedjama.com}
        {github.com/ahmedjama}
        {London, England \& Remote}

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\skill{Networks}
      {IOS, NXOS, ACI, Cumulus Linux, EOS, JUNOS, Avi, F5}
      
\skill{Protocols}
      {BGP, OSPF, EVPN, VXLAN, DNS, HTTP, TLS, SIP}

\skill{Systems}
      {Ansible, Terraform, K8s, Helm, Docker, AWS, Azure}

\skill{Development}
      {Python, Lua, Azure DevOps, Git \& GitHub}


%\skill{Robotics}
%      {Mechanical design \& prototyping, 3D modeling, OpenCV, Arduino}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Undisclosed (Contractor)}
           {Site Reliability Engineer}
           {02/2019 - present}

Maintained operational and performance monitoring responsibility for core services, networks and infrastructure across cloud (AWS, Azure) and prem environments using variety of toolsets. 

Developed CI driven Terraform framework to automate deployment and management of load balancer VIPs in Avi Vantage Platform.

Developed automation to stich Viptela SD-WAN to AWS transit gateway and Azure Virtual WAN

Successfully migrated datacenter from legacy Cisco Nexus 7K infrastructure to Cisco ACI environment.

Built python app to migrate 700+ domains from BlueCat to Route53 with intention to manage future changes as DNS-as-Code (Octodns)

\experience{The Hut Group}
           {Senior Network Engineer}
           {06/2018 - 02/2019}

Designed and deployed modern web-scale Data Centre network based on layer 3 leaf and spine topology with VXLAN and EVPN to provide tenant isolation and layer 2 overlay services using open networking principles and lots of automation.

Deployed new solutions such as DDoS mitigation and inter Data Centre DCI links using DWDM optical networking.

Provided ongoing mentorship of junior engineers and produce detailed design and operational documentation.  
           
\experience{Genesys}
           {Lead Network Engineer}
           {12/2016 - 06/2018}

Deployed SDN and SD-WAN networks based on Nuage Networks VCS for OpenStack.

Deployed resilient carrier grade SIP trunking solutions for cloud based contact centre solutions. 

\experience{Interactive Intelligence}
           {Lead Network Engineer}
           {04/2011 - 12/2016}

Deployed over a dozen greenfield colocation datacenter infrastructure.

Developed automation to turn up and provision customer network environments.

\experience{Telehouse Europe}
           {Data Centre Engineer}
           {11/2008 - 04/2011}

Provided high quality support to customers by resolving cases within the agreed SLAs in operationally sensitive production environments ensuring complete customer satisfaction.

\experience{Parliament Hill School}
           {Network Administrator}
           {06/2008 - 11/2008}

Managed the network infrastructure of the school. Initiated projects to renovate the schools desktop infrastructure as well making key improvements to the network infrastructure through remediation efforts.

\experience{Business Objects}
           {Quality Assurance Engineer}
           {06/2006 - 06/2007}

Created test environment (J2EE \& .NET) and was responsible for the daily build and test process.


\end{description}

\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{University of Westminster}
           {}
           {2004-2008}

BSc Hon. Computer Communications and Networks, Computer Science

\experience{Certification and training}
           {}
           {2010-Present}

AWS CSA, CCNP, Red Hat OpenShift Course, Nuage VCS, Oracle SBC, Future Leadership Training, ITIL Foundation


\end{description}

%\heading{Recent Speaking Engagements}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\squish
%
%\event{Linux.conf.au}
%      {01/2018}
%      {}
%      {Should you rewrite in Rust?}
%
%\event{GitHub Universe}
%      {10/2017}
%      {}
%      {Building a better browser engine on GitHub}
%
%\event{RustFest Kyiv}
%      {04/2017}
%      {Keynote lecture}
%      {Spreading Rust}
%
%\hfill \small ...and more at https://edunham.net/pages/talks.html

\end{document}
